Benchmarking Python Deep Learning Frameworks\\ for Language Modeling on GPUs

### 2016-12-14 paper/main.tex
slightly better

\paragraph{Theano}
In contrast to DyNet and TensorFlow, Theano is ``lower-level'' in that it requires that the programmer define the shared variables propagation steps, and so on manually. Theano therefore offers a great deal of control and flexibility in model implementation, which is a benefit if one is implementing neural net layers not supported by other frameworks.

@@

\section{Conclusion}
We implemented a simple language modeling task in three deep learning frameworks and measured their performance when run on a GPU. We found that DyNet converged faster than TensorFlow or Theano, but performance analysis on a fine-grained level showed that all frameworks used the underlying GPU resources with comparable efficiency. Through our experience implementing language models in these frameworks, we also found that efficiency is only one of several factors researchers should consider in choosing a deep learning framework. Users should also consider ease of installation and use, level of support available, and the suitability of the framework for their particular task.

>>>>

\paragraph{Theano}
In contrast to DyNet and TensorFlow, Theano is ``lower-level'' in that it requires that the programmer define the shared variables propagation steps, and so on manually.\footnote{An example of the relative implementation complexity can be seen in code for the LSTM Theano tutorial at \url{http://deeplearning.net/tutorial/lstm.html}.} Theano therefore offers a great deal of control and flexibility in model implementation, which is a benefit if one is implementing neural net layers not supported by other frameworks.

@@

\section{Conclusion}
We implemented a simple language modeling task in three deep learning frameworks and measured their performance when run on a GPU. We found that DyNet converged faster than TensorFlow or Theano, but performance analysis on a fine-grained level showed that all frameworks used the underlying GPU resources with comparable efficiency.

Through our experience implementing language models in these frameworks, we also found that efficiency is only one of several factors researchers should consider in choosing a deep learning framework. Users should also consider ease of installation and use, level of support available, and the suitability of the framework for their particular task.
